Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-25 analysis/paper/paper.Rmd
Add Table 1

library(bookdown)
library(knitr)
library(flextable)
library(rice.awd.pests)
library(ggpubr)
```

@@

```{r N-management, }
regulartable(N_management, col_keys = c("Nitrogen treatment",
                                        "Year", 
                                        "Total N (kg/ha)",
                                        "Basal",
                                        "Tillering",
                                        "Panicle Initiation")
             )
```

>>>>

# table captions
tn <- local({
  i = 0
  function(x) {
    i <<- i + 1
    paste('\n\nTable ', i, ': ', x, sep = '')
    # The : before Table tells pandoc to wrap your caption in <caption></caption>
  }
})
knitr::knit_hooks$set(tab.cap = function(before, options, envir) {
  if (!before)
    tn(options$tab.cap)
})
default_output_hook = knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
  if (is.null(options$tab.cap) == F)  
    x
  else
    default_output_hook(x,options)
})

library(bookdown)
library(knitr)
library(flextable)
library(ggpubr)
library(officer)
library(rice.awd.pests)
library(xtable)
```

@@

```{r N-management, tab.cap="Nitrogen application rates for 2015 and 2016. Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N~0~), 100 kg per ha N (N~1~) and 180 kg per ha N (N~2~). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N~3~) and 180 kg per ha N (N~4~). Treatments were applied in splits, basal, tillering and panicle initiation growth stages."}

N_management <- tibble::tibble(Year = integer())

N_management <-
  tibble::add_row(N_management,
                  Year = as.integer(c(2015,
                                      2015,
                                      2015,
                                      2016,
                                      2016)))

N_management$`Total N` <- as.integer(c(0,
                                                100,
                                                120,
                                                60,
                                                180))

N_management$Basal <- as.integer(c(0,
                                   60,
                                   60,
                                   30,
                                   60))

N_management$Tillering <- as.integer(c(0,
                                       20,
                                       30,
                                       30,
                                       60))

N_management$`Panicle\nInitiation` <- as.integer(c(0,
                                                   20,
                                                   30,
                                                   0,
                                                   60))

N_management <- xtable(N_management)
N_management <- xtable_to_flextable(x = N_management, NA.string = "-")

N_management <- flextable::display(
  N_management,
  i = 1,
  col_key = "rowname",
  pattern = "{{val}}{{pow}}",
  part = "body",
  formatters = list(val ~ as.character("N"), pow ~ as.character("0")),
  fprops = list(pow = fp_text(
    vertical.align = "subscript", font.size = 8
  ))
)

N_management <- flextable::display(
  N_management,
  i = 2,
  col_key = "rowname",
  pattern = "{{val}}{{pow}}",
  part = "body",
  formatters = list(val ~ as.character("N"), pow ~ as.character("1")),
  fprops = list(pow = fp_text(
    vertical.align = "subscript", font.size = 8
  ))
)

N_management <- flextable::display(
  N_management,
  i = 3,
  col_key = "rowname",
  pattern = "{{val}}{{pow}}",
  part = "body",
  formatters = list(val ~ as.character("N"), pow ~ as.character("2")),
  fprops = list(pow = fp_text(
    vertical.align = "subscript", font.size = 8
  ))
)

N_management <- flextable::display(
  N_management,
  i = 4,
  col_key = "rowname",
  pattern = "{{val}}{{pow}}",
  part = "body",
  formatters = list(val ~ as.character("N"), pow ~ as.character("3")),
  fprops = list(pow = fp_text(
    vertical.align = "subscript", font.size = 8
  ))
)

N_management <- flextable::display(
  N_management,
  i = 5,
  col_key = "rowname",
  pattern = "{{val}}{{pow}}",
  part = "body",
  formatters = list(val ~ as.character("N"), pow ~ as.character("4")),
  fprops = list(pow = fp_text(
    vertical.align = "subscript", font.size = 8
  ))
)

N_management <- add_header(N_management,
                           Year = "Year",
                           Tillering = "Application Rate (kg/ha)")

N_management <- merge_v(N_management, part = "header")

N_management <- autofit(N_management)
N_management

```
